\ttitle

### 2013-11-07 Chapters/Chapter4/data_gathering.tex
WIP

>>>>

For the experiments we used a HTC Sensation XE smartphone as recording device.
The activities were recorded using a free Android application \cite{sensorlogger}.
This application was chosen for its convenient data format of the sensor recording and its regularity of the sampling interval.
Table~\ref{tab:recorded_metrics} lists the recorded metrics.
For our expiments we used the data for the accelerometer, magnatief field and rotation.

\begin{center}\begin{table}
  \begin{tabulary}{\textwidth}{|l|L|c|c|}
    \hline
    Metric & Description & Units of measure & Typical range \\
    \hline \hline
    Accelerometer & Acceleration force along each axis. & $m/s^2$ & $-20$ -- $20$ \\
    \hline
    Gravity & Force of gravity along each axi.s & $m/s^2$ & $-10$ -- $10$\\
    \hline
    Gyroscope & & $rad/s$ & $-15$ -- $15$\\
    \hline
    Light & Light sensitive sensor at the front of the phone. & & $0$ -- $10000$ \\
    \hline
    Linear acceleration & & $m/s^2$ & $-20$ -- $20$ \\
    \hline
    Magnetic field & Geomagnetic field strength along each axis. & $\mu T$ & $-60$ -- $60$ \\
    \hline
    Orientation & & & $-100$ -- $360$ \\
    \hline
    Rotation & & & $-1$ -- $1$\\
    \hline
  \end{tabulary}
  \caption{Measured metrics. The set of axis is always the triple (x, y, z) direction.}
  \label{tab:recorded_metrics}
\end{table}\end{center}

### 2013-11-07 Chapters/Chapter4/model_construction.tex
WIP

% !TEX root = ../../main.tex
\section{Model Construction: Incremental SVDD}\label{sec:method_model_construction}
After the data is collected and pre-processed (or in the case of the artificial data sets: generated), we construct an online incremental sliding window algorithm.
We follow the \gls{svcpd} method by Camci \cite{camci2010change} and the \gls{isvdd} implementation by Tax and Laskov \cite{tax2003online}.
That latter algorithm combines the techniques of online, unsupervised, and incremental learning methods with the earlier introduced \gls{oc-svm} algorithm \gls{svdd}.
The method is initialized with a fixed window length and then in every step a new data object is added to and the oldest data object is removed from the working set.

>>>>

% !TEX root = ../../main.tex
\section{Model Construction: Incremental SVDD}\label{sec:method_model_construction}
After the data is collected and pre-processed (or in the case of the artificial data sets: generated), we construct an online incremental sliding window algorithm.
We follow the \gls{svcpd} method by Camci \cite{camci2010change} and the \gls{isvdd} implementation by Tax and Laskov \cite{tax2003online}.
The latter algorithm combines the techniques of online, unsupervised, and incremental learning methods with the earlier introduced \gls{oc-svm} algorithm \gls{svdd}.
The method is initialized with a fixed window length and then in every step a new data object is added to and the oldest data object is removed from the working set.
